Learning Discrete Bayesian Networks from Continuous Data

### 2015-12-02 Fig15.tex
A partial update according to Mykel's comments

\begin{tikzpicture}
		\begin{axis}[
			view={0}{90},
			enlargelimits=0,
			zmin=0.0, zmax=1.0,
			xlabel=$C$,
			ylabel=$E$,
			colorbar,
			point meta min=0, point meta max=1,
			colormap={}{ gray(0cm)=(1); gray(1cm)=(0);},
			colorbar style={
			        ytick={0,0.2,...,1.01},
			        ylabel={probability density$ \times 10^{-1}$},
			        y label style={at={(axis description cs:6.5,0.5)},rotate=180,anchor=north},
			        yticklabels={\num{0.00},\num{0.20},\num{0.40},\num{0.60},\num{0.80},$\geq 1$},
			        yticklabel style={
			            text width=2.5em,
			            align=right,
			            /pgf/number format/.cd,
			                fixed,
			                fixed zerofill
			        }
			    }
			]

>>>>

\begin{tikzpicture}
		\begin{axis}[
			view={0}{90},
			enlargelimits=0,
			zmin=0.0, zmax=1.0,
			xlabel=$C$,
			ylabel=$E$,
			colorbar,
			point meta min=0, point meta max=1,
			colormap={}{ gray(0cm)=(1); gray(1cm)=(0);},
			colorbar style={
			        ytick={0,0.2,...,1.01},
			        ylabel={probability density$ \times 10^{-1}$},
			        y label style={at={(axis description cs:4.5,0.5)},rotate=180,anchor=north},
			        yticklabels={\num{0.00},\num{0.20},\num{0.40},\num{0.60},\num{0.80},$\geq 1$},
			        yticklabel style={
			            text width=2.5em,
			            align=right,
			            /pgf/number format/.cd,
			                fixed,
			                fixed zerofill
			        }
			    }
			]

### 2015-12-02 Fig16.tex
A partial update according to Mykel's comments

\begin{tikzpicture}
		\begin{axis}[
			view={0}{90},
			enlargelimits=0,
			zmin=0.0, zmax=1.0,
			xlabel=$H$,
			ylabel=$E$,
			colorbar,
			point meta min=0, point meta max=0.4,
			colormap={}{ gray(0cm)=(1); gray(1cm)=(0);},
			colorbar style={
			        ytick={0,0.08,...,0.41},
			        ylabel={probability density$ \times 10^{-1}$},
			        y label style={at={(axis description cs:6.5,0.5)},rotate=180,anchor=north},
			        yticklabel style={
			            text width=2.5em,
			            align=right,
			            /pgf/number format/.cd,
			                fixed,
			                fixed zerofill
			        }
			    }
			]

>>>>

\begin{tikzpicture}
		\begin{axis}[
			view={0}{90},
			enlargelimits=0,
			zmin=0.0, zmax=1.0,
			xlabel=$H$,
			ylabel=$E$,
			colorbar,
			point meta min=0, point meta max=0.4,
			colormap={}{ gray(0cm)=(1); gray(1cm)=(0);},
			colorbar style={
			        ytick={0,0.08,...,0.41},
			        ylabel={probability density$ \times 10^{-1}$},
			        y label style={at={(axis description cs:4.5,0.5)},rotate=180,anchor=north},
			        yticklabel style={
			            text width=2.5em,
			            align=right,
			            /pgf/number format/.cd,
			                fixed,
			                fixed zerofill
			        }
			    }
			]

### 2015-12-02 Fig4.tex
A partial update according to Mykel's comments

\begin{tikzpicture}
		\begin{axis}[
			view={0}{90},
			enlargelimits=0,
			zmin=0.0, zmax=1.0,
			xlabel=$A$,
			ylabel=$C$,
			colorbar,
			point meta min=0, point meta max=1.2,
			colormap={}{ gray(0cm)=(1); gray(1cm)=(0);},
			colorbar style={
			        ytick={0,0.24,...,1.3},
			        ylabel={probability density $\times 10^3$},
			        y label style={at={(axis description cs:6.5,0.5)},rotate=180,anchor=north},
			        yticklabel style={
			            text width=2.5em,
			            align=right,
			            /pgf/number format/.cd,
			                fixed,
			                fixed zerofill
			        }
			    }
			]

>>>>

\begin{tikzpicture}
		\begin{axis}[
			view={0}{90},
			enlargelimits=0,
			zmin=0.0, zmax=1.0,
			xlabel=$A$,
			ylabel=$C$,
			colorbar,
			point meta min=0, point meta max=1.2,
			colormap={}{ gray(0cm)=(1); gray(1cm)=(0);},
			colorbar style={
			        ytick={0,0.3,...,1.21},
			        ylabel={probability density $\times 10^3$},
			        y label style={at={(axis description cs:4.5,0.5)},rotate=180,anchor=north},
			        yticklabel style={
			            text width=2.5em,
			            align=right,
			            /pgf/number format/.cd,
			                fixed,
			                fixed zerofill
			        }
			    }
			]

### 2015-12-02 Fig8.tex
A partial update according to Mykel's comments

    \nextgroupplot[
			view={0}{90},
			enlargelimits=0,
			zmin=0.0, zmax=1.0,
			xlabel=$E$,
			%ylabel=K,
			colorbar,
			point meta min=0, point meta max=2.5,
			colormap={}{ gray(0cm)=(1); gray(1cm)=(0);},
			colorbar style={
			        ytick={0,0.5,...,2.6},
			        ylabel={probability density $\times 10^2$},
			        y label style={at={(axis description cs:6.0,0.5)},rotate=180,anchor=north},
			        yticklabel style={
			            text width=1.5em,
			            align=right,
			           /pgf/number format/.cd,
			                fixed,
			                fixed zerofill
			        }
			    }
			]

>>>>

    \nextgroupplot[
			view={0}{90},
			enlargelimits=0,
			zmin=0.0, zmax=1.0,
			xlabel=$E$,
			%ylabel=K,
			colorbar,
			point meta min=0, point meta max=2.5,
			colormap={}{ gray(0cm)=(1); gray(1cm)=(0);},
			colorbar style={
			        ytick={0,0.5,...,2.51},
			        ylabel={probability density $\times 10^2$},
			        y label style={at={(axis description cs:3.7,0.5)},rotate=180,anchor=north},
			        yticklabel style={
			            text width=1.5em,
			            align=right,
			           /pgf/number format/.cd,
			                fixed,
			                fixed zerofill
			        }
			    }
			]
